Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-04 doc/sc2012/legion.tex
Some minor changes to the paper

Legion programs are written using logical regions, which do not commit
to any particular layout of the data or placement of the data in the machine.  At runtime,
each logical reagion has one or more {\em physical instances}.  Often
logical regions correspond to a single physical instance, but it is also common and useful
to have multiple physical copies of a logical region's contents in different parts of the machine 
to duplicate and distribute read-only data, to keep an old copy of a region to break a 
write-after-read dependence, or to allow independent, local reductions that are later combined.

>>>>

Legion programs are written using logical regions, which do not commit
to any particular layout of the data or placement of the data in the machine.  At runtime,
each logical region has one or more {\em physical instances}.  Often
logical regions correspond to a single physical instance, but it is also common and useful
to have multiple physical copies of a logical region's contents in different parts of the machine 
to duplicate read-only data, to keep an old copy of a region to break a 
write-after-read dependence, or to allow independent, local reductions that are later combined.

### 2012-05-04 doc/sc2012/mapping.tex
Some minor changes to the paper

\subsection{Mapping Interface}
\label{sec:mapinterface}
A mapper is any object that implements the mapping interface.  The mapping interface
consists of ten function calls that the runtime will make to request direction from
the programmer about how a program should be executed.  To aid in performing the 
decisions made in these calls the mapper has access to a simple 
interface for inspecting the properties of the machine on which it is running.  This includes 
information about all the processors and their kinds (i.e. CPU,GPU), as well as the memories visible
to each processor and their latencies and bandwidths.  For brevity we only
discuss three of the mapping interface calls.

>>>>

\subsection{Mapping Interface}
\label{sec:mapinterface}
A mapper is any object that implements the mapping interface.  The mapping interface
consists of ten function calls that the runtime will make to request direction from
the mapper about how a program should be executed.  To aid in performing the 
decisions made in these calls the mapper has access to a simple 
interface for inspecting the properties of the machine on which it is running.  This includes 
information about all the processors and their kinds (i.e. CPU,GPU), as well as the memories visible
to each processor and their latencies and bandwidths.  For brevity we only
discuss three of the mapping interface calls.

### 2012-05-04 doc/sc2012/soop.tex
Some minor changes to the paper

We can identify all mappoing dependences between sibling tasks and place tasks
in the correct place in the region tree in amortized time ${\cal O}(d)$ per region,
where $d$ is the depth of the region tree.  For region $r'$ an argument of task $t'$, the analysis
walks the unique path in the region forest from a root to $r'$.  For each node $m$
on the walk from the root to $r'$ the following actions are taken:
\begin{itemize}
\item If $m$ is a region with multiple child partitions and $m'$ is the child on the
path to $r'$, then any task in a subtree of $m$ other than $m'$ on which $t'$ depends 
is moved to $m$.

@@

The region tree is also used to hold mapping information.  Each logical region $r$ maintains a
list of its physical instances and which sibling tasks are using which
instances and with what permissions.  The important correctness
property established by stage 1 is that all
tasks $t$ depends on map before $t$ maps and no task that depends on
$t$ maps before $t$ finishes mapping.  Thus, the region tree at the
moment $t$ maps contains a consistent view of what the state of memory
will be after $t$'s dependence predecessors execute.

There are two steps to mapping a region $r$ used by
task $t$.  First, the mapper must ensure there is at least one {\em valid}
physical instance of $r$.  If an instance of a subregion of $r$ has been written by a previous task,
for example, it is necessary to copy that subregion back to an instance of the parent $r$ so that $t$
sees the correct data. In the second step, the mapping interface selects one of the
valid physical instances of $r$ or creates a new one.  
We focus here on the first step; the mapping interface is discussed further in Section~\ref{sec:mapping}.

@@

Figure~\ref{fig:depexamp:c} shows part of the mapping of task {\tt update\_voltages[0]}; we focus
only on the shared nodes.
Because the immediately preceding {\tt distribute\_charges} tasks all performed the same reduction
on the shared and ghost nodes they were allowed to run in parallel.  But {\tt update\_voltages[0]}
needs read/write privilege for {\tt pieces[0].rn\_shr}, which forces all of the reductions to be merged
back to an instance of the {\tt all-shared} nodes region, from which a new instance of {\tt pieces[0].rn\_shr} is copied and used by {\tt update\_voltages[0]}.

>>>>

We can identify all mapping dependences between sibling tasks and place tasks
in the correct place in the region tree in amortized time ${\cal O}(d)$ per region,
where $d$ is the depth of the region tree.  For region $r'$ an argument of task $t'$, the analysis
walks the unique path in the region forest from a root to $r'$.  For each node $m$
on the walk from the root to $r'$ the following actions are taken:
\begin{itemize}
\item If $m$ is a region with multiple child partitions and $m'$ is the child on the
path to $r'$, then any task in a subtree of $m$ other than $m'$ on which $t'$ depends 
is moved to $m$.

@@

The region tree is also used to hold mapping information.  Each logical region $r$ maintains a
list of its physical instances and which sibling tasks are using which
instances and with what permissions.  The important correctness
property established by stage 1 is that all
tasks which $t$ may depend on map before $t$ maps and no task that may depend on
$t$ maps before $t$ finishes mapping.  Thus, the region tree at the
moment $t$ maps contains a consistent view of what the state of memory
will be after $t$'s dependence predecessors execute.

There are two steps to mapping a region $r$ used by
task $t$.  First, the mapper must ensure there is at least one {\em valid}
physical instance of $r$ for $t$ to use.  If an instance of a subregion of $r$ has been written by a previous task,
for example, it is necessary to copy that subregion back to an instance of the parent $r$ so that $t$
sees the correct data. In the second step, the mapping interface selects one of the
valid physical instances of $r$ or creates a new one.  
We focus here on the first step; the mapping interface is discussed further in Section~\ref{sec:mapping}.

@@

Figure~\ref{fig:depexamp:d} shows part of the mapping of task {\tt update\_voltages[0]}; we focus
only on the shared nodes.
Because the immediately preceding {\tt distribute\_charges} tasks all performed the same reduction
on the shared and ghost nodes they were allowed to run in parallel.  But {\tt update\_voltages[0]}
needs read/write privilege for {\tt pieces[0].rn\_shr}, which forces all of the reductions to be merged
back to an instance of the {\tt all-shared} nodes region, from which a new instance of {\tt pieces[0].rn\_shr} is copied and used by {\tt update\_voltages[0]}.
